SiO Molecular Jets around young stars - A numerical perspective

### 2013-10-02 PAPER/ms_final_bv.tex
Added more text on cooling modes comparison

The dynamical states for each of this cooling prescription are then 
post-processed to obtain integrated J = 2-$>$1 SiO emission
maps shown in figure~\ref{fig:coolcmpsio}. The differences in dynamical
features are also reflected in the corresponding SiO emission
maps. These maps are obtained assuming an angle of inclination of
90$^\circ$ using the top hat abundance
profile with $\delta = 1$ and they are further convolved with a beam
having a FWHM of 2.5\arcsec. The
emission features in jet with atomic and power-law cooling prescription do not have
such a well defined lobe structure. For example, the emission from the jet with atomic
cooling is mainly coming from regions close to R,Z = $\pm$
10,80. In fact the emission from this region seems to be stronger than
that coming from the conical jet head. In case of the jet with
power-law cooling the emission seems to be mostly coming from the
internal knots. The thin density layer formed at the interface of jet
and the ambient medium do not show indication of any emission. 
The emission coming from jets with
tabulated and molecular cooling show a distinctive outflow lobe which
is typically observed in case of young molecular outflows.
SiO emission coming from internal knots in these jets also show a
distinctive turbulent pattern consistent with observations.

Bulk of emission comes from cooling instabilities.
figure nos. 2 -- Simulated images, emission maps for eta = 10.
\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/jetplt1_1010.png}
 \caption{Jet Volume Density for different cooling modes with
   $\eta$ = 10 and $\beta$ = 10.}
\label{fig:coolcmpdyn}
\end{figure*}

>>>>

The dynamical states for each of this cooling prescription are then 
post-processed to obtain integrated J = 2-$>$1 SiO emission
maps shown in figure~\ref{fig:coolcmpsio}. The differences in dynamical
features are also reflected in the corresponding SiO emission
maps. These maps are obtained assuming an angle of inclination of
90$^\circ$ using the top hat abundance
profile with $\delta = 1$ and they are further convolved with a beam
having a FWHM of 2.5\arcsec. The
emission features in jet with atomic and power-law cooling prescription do not have
such a well defined lobe structure. For example, the emission from the jet with atomic
cooling is mainly coming from regions close to R,Z = $\pm$
10,80. In fact the emission from this region seems to be stronger than
that coming from the conical jet head. In case of the jet with
power-law cooling the emission seems to be mostly coming from the
internal knots. The thin density layer formed at the interface of jet
and the ambient medium do not show indication of any emission. 
The emission coming from jets with
tabulated and molecular cooling show a distinctive outflow lobe which
is typically observed in case of young molecular outflows.
SiO emission coming from internal knots in these jets also show a
distinctive turbulent pattern consistent with
observations. Additionally, strong emission also comes from the
condensation formed at the primary bow shock due to thermal
instability. 
%

In summary, different cooling prescriptions does influence the
dynamics of MHD jet propagation in particular the thickness and
structure of the primary bow shock. These dynamical differences are
also reflected in SiO emission maps and spectra. Emission maps
obtained from molecular cooling show a distinctive outflow lobe
structure which is consistent with observations. The properties of 
molecular cooling flows are described in details in the next section.

\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/jetplt1_1010.png}
 \caption{Jet Volume Density for different cooling modes with
   $\eta$ = 10 and $\beta$ = 10.}
\label{fig:coolcmpdyn}
\end{figure*}
